Fig2

### 2020-02-21 analysis/figure-2.Rmd
smaller font

makebargraph <- function(whichtissue, myylab, lowlim, higherlim){
  p <- allDEG %>%
    filter(tissue == whichtissue,
           comparison != "control_bldg") %>%
  ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge") +
    facet_grid(tissue~sex) +
    theme_B3() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs(x = "Sequential parental care stage comparisons", 
         y = myylab,
         subtitle = " ") +
  scale_fill_manual(values = allcolors,
                       name = " ",
                       drop = FALSE) +
  scale_color_manual(values = allcolors) +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
            position = position_dodge(width = 1),
            size = 2.5, color = "black")  +
  ylim(lowlim, higherlim)
  return(p)
}

@@

```{r fig2, fig.width=7, fig.height=6}
# hyp
p1 <- makebargraph("hypothalamus","DEGs", 0, 1250) + theme(axis.text.x = element_blank(), 
                                                               axis.title.x = element_blank())

@@

bcd <- plot_grid(p1,p2,p3, nrow = 3, rel_heights = c(1.2,1,1.5), labels = c("b", "c", "d"), label_size = 12)

@@

plot_grid(expdesign, bcd, labels = c("a", " "), label_size = 12, nrow = 2, rel_heights = c(0.2,1))

@@

makenewbargraph <- function(whichtissue, whichsex,  whichcomparison, lowlim, higherlim){
  p <- allDEG2 %>%
    filter(tissue == whichtissue,
           comparison == whichcomparison,
           sex == whichsex) %>%
    ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge", drop = FALSE) +
    theme_B3() +
    theme(legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs( y = whichtissue) +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
           position = position_dodge(width = 1),
           size = 2.5, color = "black")  + 
      ylim(lowlim, higherlim) +
  scale_fill_manual(values = allcolors, name = "higher in")   + 
    theme(axis.text.x = element_blank()) 
  return(p)
}

@@

hypothesisbars <-  plot_grid(b112131, b122232, c112131, c122232, nrow = 1, rel_widths = c(1.3, 1, 1.1, 1),
          labels = c("b", " ", "c", " "), label_size = 12)

@@

plot_grid(expdesign2, hypothesisbars, rel_heights = c(0.5,1), nrow = 2, labels = c("a", " "), label_size = 12)
```

>>>>

makebargraph <- function(whichtissue, myylab, lowlim, higherlim){
  p <- allDEG %>%
    filter(tissue == whichtissue,
           comparison != "control_bldg") %>%
  ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge") +
    facet_grid(tissue~sex) +
    theme_B3() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs(x = "Sequential parental care stage comparisons", 
         y = myylab,
         subtitle = " ") +
  scale_fill_manual(values = allcolors,
                       name = " ",
                       drop = FALSE) +
  scale_color_manual(values = allcolors) +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
            position = position_dodge(width = 1),
            size = 2, color = "black")  +
  ylim(lowlim, higherlim)
  return(p)
}

@@

```{r fig2, fig.width=6, fig.height=5}
# hyp
p1 <- makebargraph("hypothalamus","DEGs", 0, 1250) + theme(axis.text.x = element_blank(), 
                                                               axis.title.x = element_blank())

@@

bcd <- plot_grid(p1,p2,p3, nrow = 3, rel_heights = c(1.2,1,1.5), labels = c("b", "c", "d"), label_size = 8)

@@

plot_grid(expdesign, bcd, labels = c("a", " "), label_size = 8, nrow = 2, rel_heights = c(0.2,1))

@@

makenewbargraph <- function(whichtissue, whichsex,  whichcomparison, lowlim, higherlim){
  p <- allDEG2 %>%
    filter(tissue == whichtissue,
           comparison == whichcomparison,
           sex == whichsex) %>%
    ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge", drop = FALSE) +
    theme_B3() +
    theme(legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs( y = whichtissue) +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
           position = position_dodge(width = 1),
           size = 2, color = "black")  + 
      ylim(lowlim, higherlim) +
  scale_fill_manual(values = allcolors, name = "higher in")   + 
    theme(axis.text.x = element_blank()) 
  return(p)
}

@@

hypothesisbars <-  plot_grid(b112131, b122232, c112131, c122232, nrow = 1, rel_widths = c(1.3, 1, 1.1, 1),
          labels = c("b", " ", "c", " "), label_size = 8)

@@

plot_grid(expdesign2, hypothesisbars, rel_heights = c(0.5,1), nrow = 2, labels = c("a", " "), label_size = 8)
```
